Plant-pollintor networks worldwide are composed by the same specific building

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to extract all motif combinations in the three networks with the highest number of links). To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively. Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not. To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared ($\sum_{k=1}^{53250} n_k^O$): $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$. Consequently, $\sum_{k=1}^{53250} p_k^O = 1$. To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$). Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ is equal to the product of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$. To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$. We controlled the variation at the network level and assessed the average value of $n_i(x,\alpha)$ by fitting a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers. To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].

>>>>

Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to extract all motif combinations in the three networks with the highest number of links). To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively. Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not. To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$. To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$). Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ is equal to the product of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$. To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$. Then, by controlling the variation at the network level, we assessed the average value of $n_i(x,\alpha)$, $E\left [ n_i(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha)=E\left [ n_i(x,\alpha) \right ]/\sum_{k}E\left [ n_i(k,\alpha) \right ]$. To obtain $E\left [ n_i(x,\alpha) \right ]$, we fitted a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers. To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
